
\section{Product Perspective}

ePurano is a new application designed to create a marketplace for peer-to-peer transactions of secondhand items. Unlike traditional e-commerce platforms, ePurano focuses specifically on pre-owned goods, promoting sustainability and cost savings for users. The platform will be standalone but will integrate with various third-party services for payment processing, user authentication, and messaging.

\section{Product Functions}

\subsection{User Functions}

\begin{itemize}
    \item \textbf{User Registration and Authentication}: Users can create accounts, log in, and manage their profiles.
    \item \textbf{Item Listings}: Users can list items for sale, including uploading images and descriptions.
    \item \textbf{Search and Filter}: Buyers can search and filter listings by categories, price range, and location.
    \item \textbf{Secure Messaging}: Users can communicate securely within the platform to negotiate and finalize transactions.
    \item \textbf{Payment Processing}: Integrated payment gateway for secure transactions.
    \item \textbf{Review System}: Users can leave reviews and ratings for each other to build trust within the community.
\end{itemize}

\subsection{Admin Functions}

\begin{itemize}
    \item \textbf{User Management}: Admins can manage user accounts, including registration approvals, suspensions, and deletions.
    \item \textbf{Content Moderation}: Admins can review and moderate listings, messages, and reviews to ensure compliance with platform policies.
    \item \textbf{Platform Analytics}: Admins can access and analyze platform usage data to improve services.
    \item \textbf{Customer Support}: Admins provide support to users, addressing any issues or concerns.
\end{itemize}

\section{User Characteristics}

\subsection{Users}

\begin{itemize}
    \item \textbf{Sellers}: Individuals looking to sell secondhand items in a user-friendly and reliable environment.
    \item \textbf{Buyers}: Individuals seeking to purchase secondhand goods at competitive prices.
\end{itemize}

\subsection{Administrators}

\begin{itemize}
    \item \textbf{Platform Managers}: Staff responsible for managing the platform, handling user support, and ensuring smooth operation.
\end{itemize}

\section{Constraints}

Key constraints for the development and operation of ePurano include:

\begin{itemize}
    \item \textbf{Budget}: Limited funding for development and initial marketing.
    \item \textbf{Time}: Tight deadlines to launch the MVP (Minimum Viable Product).
    \item \textbf{Technological}: Integration with third-party services must comply with their APIs and terms of service.
    \item \textbf{Regulatory}: Compliance with data protection regulations and e-commerce laws.
\end{itemize}

\section{Assumptions and Dependencies}

\begin{itemize}
    \item \textbf{User Adoption}: Successful adoption by users is critical for the platform's success.
    \item \textbf{Third-Party Services}: Dependence on external services for payment processing, user authentication, and messaging.
    \item \textbf{Internet Access}: Users must have internet access to use the platform.
    \item \textbf{Device Compatibility}: The platform must be compatible with modern web browsers and mobile devices.
\end{itemize}

By considering these aspects, the development team can ensure that ePurano meets the needs of its users and operates smoothly within its constraints and dependencies.
